Pretty darn good control: when are approximate solutions better than approximate models

### 2023-06-26 manuscript/manuscript.Rmd
added ppo policy appendix

Policies obtained from the PPO algorithm can be ‘‘noisy’’ as their optimization algorithm is randomized (see, e.g. App. \textbf{TBD} for visualizations of these policies).
We perform some interpolation using a Gaussian process regressor in order to de-noise these policies.
Specifically, we use the *GaussianProcessRegressor* object of the *sklearn* Python library with a kernel given by
\begin{align*}
  \text{RBF}(\text{length scale = 10}) + \text{WhiteNosie}(\text{noise level = 0.1}).
\end{align*}
This interpolation method is applied to scatter data of the PPO policy evaluated on 3 different grids:
One $51\times 51 \times 5$, one $51\times 5 \times 51$ and one $5\times 51 \times 51$ grid on $(X,Y,Z)$ states.\footnote{
The raw dataset is found at \textbf{TBD} in the repository with the source code and data linked above.
Scatter plots visualizing this policy are shown in App. \textbf{TBD}.
}
The length scale and noise level values of this kernel were chosen arbitrarily---no hyperparameter tuning was needed to produce satisfactory interpolation, as will be shown in the results section.

@@

We will visualize the results concerning the last scenario considered (‘‘3 species, 2 of which harvested, and a time-varying parameter’’) in this section, leaving the other cases for the appendix.
This is the most complex scenario considered and where our results show the most compelling advantage of DRL methods with respect to classical strategies.

@@

In the main text we focused on the non-stationary model (‘‘three species, two fisheries, non-stationary’’ in Table 1) for the sake of space and because our results were most compelling there.
Here we present the reward distributions for the other models considered.
```{r}
summary_32 <- read_csv("manuscript_data/comparison_3-2-const_300.csv.xz") %>%
  mutate(strategy=recode(strategy, "PPO+GP"="PPO_GP")) %>%
  arrange(strategy)
summary_31 <- read_csv("manuscript_data/comparison_3-1_300.csv.xz") %>%
  mutate(strategy=recode(strategy, "PPO+GP"="PPO_GP")) %>%
  arrange(strategy)
summary_11 <- read_csv("manuscript_data/comparison_1-1_100.csv.xz") %>%
  mutate(strategy=recode(strategy, "PPO+GP"="PPO_GP")) %>%
  arrange(strategy)
```

@@

>>>>

Policies obtained from the PPO algorithm can be ‘‘noisy’’ as their optimization algorithm is randomized (see, e.g. App. B for visualizations of the PPO policy in the ‘‘3 species, 2 fisheries, non-stationary’’ case).
We perform some interpolation using a Gaussian process regressor in order to de-noise these policies.
Specifically, we use the *GaussianProcessRegressor* object of the *sklearn* Python library with a kernel given by
\begin{align*}
  \text{RBF}(\text{length scale = 10}) + \text{WhiteNosie}(\text{noise level = 0.1}).
\end{align*}
This interpolation method is applied to scatter data of the PPO policy evaluated on 3 different grids:
One $51\times 51 \times 5$, one $51\times 5 \times 51$ and one $5\times 51 \times 51$ grid on $(X,Y,Z)$ states.\footnote{
The raw dataset is found at \textbf{TBD} in the repository with the source code and data linked above.
Scatter plots visualizing this policy are shown in App. \textbf{TBD}.
}
The length scale and noise level values of this kernel were chosen arbitrarily---no hyperparameter tuning was needed to produce satisfactory interpolation, as will be shown in the results section.

@@

We will visualize the results concerning the last scenario considered (‘‘3 species, 2 of which harvested, and a time-varying parameter’’) in this section, leaving the other cases for App. A.
This is the most complex scenario considered and where our results show the most compelling advantage of DRL methods with respect to classical strategies.

@@

In the main text we focused on the non-stationary model (‘‘three species, two fisheries, non-stationary’’ in Table 1) for the sake of space and because our results were most compelling there.
Here we present the reward distributions for the other models considered---the three stationary models, lines 1-3 in Table 1.

```{r}
summary_32 <- read_csv("manuscript_data/comparison_3-2-const_300.csv.xz") %>%
  mutate(strategy=recode(strategy, "PPO+GP"="PPO_GP")) %>%
  arrange(strategy)
summary_31 <- read_csv("manuscript_data/comparison_3-1_300.csv.xz") %>%
  mutate(strategy=recode(strategy, "PPO+GP"="PPO_GP")) %>%
  arrange(strategy)
summary_11 <- read_csv("manuscript_data/comparison_1-1_100.csv.xz") %>%
  mutate(strategy=recode(strategy, "PPO+GP"="PPO_GP")) %>%
  arrange(strategy)
```

@@

## PPO policy function for non-stationary model

In the main text, Fig. \ref{fig:gpp-policy}, we presented a visualization of the PPO+GP policy function obtained for the ‘‘three species, two fisheries, non-stationary’’ model.
This policy function is a Gaussian process regression of scatter data of the PPO policy function.
In Fig. \ref{fig:ppo-policy} we present a representation of this scatter data in a similar format as Fig. \ref{fig:gpp-policy}.

\begin{figure}
  \centering
  \includegraphics[scale=0.35]{figures/ppo-policy.jpeg}
  \caption{Plots of the PPO policy $\pi_{\text{PPO}}$ along several relevant axes. Here $M_X$ and $M_Y$ are the $X$ and $Y$ components of the policy function. The values of the plots are generated in the following way: For each variable $X$, $Y$, and $Z$, the time-series of evaluation episodes are used to generate a window of typical values that variable attains when controlled by $\pi_{\text{PPO}}$. Then, for each plot either $X$ or $Y$ was evaluated on 100 values in $[0,1]$ along the $x$ axis, while the other variables (resp. $Y$ and $Z$, or $X$ and $Z$) were varied within the typical window computed before. Within this window, 5 values are used. The value of one of the latter two variables were visualized as color. This scatter data was used as an input to generate $\pi_{\text{PPO+GP}}$, visualized in the main text.}
  \label{fig:ppo-policy}
\end{figure}
